---
title:
runtime: shiny
output: html_document
keep_md: no
---
  
**Absolute & Relative Displacement**
```{r engine='bash', echo=FALSE}
val1=`cat PROJECTDIR/subjects/SUBID/sessionNO/mcflirt_data/TASK_data_abs_mean.rms`
echo "Mean Absolute Displacement : $val1 mm" 
val2=`cat PROJECTDIR/subjects/SUBID/sessionNO/mcflirt_data/TASK_data_rel_mean.rms`
echo "Mean Relative Displacement : $val2 mm"
```

**List of All Outlier Volumes (e002)**
```{r engine='bash', echo=FALSE}
cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e002_outliers_volumes.txt
```

**Percentage of Motion (FD, DVARS & SN) Outlier Volumes**
```{r engine='bash', echo=FALSE}
num_outliers=`cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/SUBID_all_outliers.txt | wc -l`
num_volumes=`fslval PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e002.nii.gz dim4`
percent_outliers=`echo ${num_outliers} ${num_volumes}|awk '{printf "%3.2f", $1/$2}'`
echo "${percent_outliers}%"
```
**FD Volume Outliers for e002**
```{r engine='bash', echo=FALSE}
cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e002_fd_spike_vols
```
**FD Volume Outliers for Optimally Combined Time Series**
```{r engine='bash', echo=FALSE}
cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e00213_tsoc_fd_spike_vols
```
**FD Volume outliers for Denoised Time Series**
```{r engine='bash', echo=FALSE}
cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e00213_medn_fd_spike_vols
```

**DVARS Volume Outliers for e002**
```{r engine='bash', echo=FALSE}
cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e002_dvars_spike_vols
```
**DVARS Volume Outliers for Optimally Combined Time Series**
```{r engine='bash', echo=FALSE}
cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e00213_tsoc_dvars_spike_vols
```
**DVARS Volume Outliers for Denoised Time Series**
```{r engine='bash', echo=FALSE}
cat PROJECTDIR/subjects/SUBID/sessionNO/TASK/TASK_e00213_medn_dvars_spike_vols
```

